---
page_title: "mock_redcap_report"
output: html_document
---


```{r setup, include = FALSE}

knitr::opts_chunk$set(
  echo = TRUE,    # Hide the source code by default in the output
  warning = FALSE, # Hide warnings
  message = FALSE, # Hide system messages
  fig.width = 8,   # Default figure width in inches
  fig.height = 6   # Default figure height in inches
)

# Set global R options if needed
options(digits = 3) 

library(tidyverse)
library(gtsummary)
library(gt)

```


# Quality of Life and Chronic Disease    

## REDCap Data Summary  

```{r}
redcap_subjects <- read_csv("data/mock_redcap_subjects.csv")
redcap_subjects %>%
  gt::gt_preview()

redcap_visits <- read_csv("data/mock_redcap_visits.csv")
redcap_visits %>%
  gt::gt_preview()

```

We have enrolled `r nrow(redcap_subjects)` participants, and we have captured `r nrow(redcap_visits)` follow-up visits among participants.


## Quality of Life Measured Among Participants  

We have measured quality of life across all participants and visits:

```{r}
redcap_visits %>%
  ggplot(data = .) +
  geom_histogram(aes(x = measured_QOL), binwidth = 1, fill = "white", color = "red", alpha = 0.5)

```


## Subject Demographics  

```{r}

redcap_subjects %>%
  mutate(age_years = lubridate::time_length(interval(enrollment_date, birth_date), "years")) %>%
  select(rural_residence, age_years, smoker, diabetes_mellitus, cad, copd) %>%
  gtsummary::tbl_summary(data = ., by = rural_residence) %>%
  gtsummary::add_overall() %>%
  gtsummary::add_p() %>%
  gtsummary::modify_spanning_header(gtsummary::all_stat_cols() ~ "**Rural Residence**")


```


## Association Between Quality-of-Life Outcome & Exposures of Interest  

- We used boxplots to assess the association between measured QOL and rural residence:  

```{r}
redcap_subjects %>%
  left_join(redcap_visits, by = "subject_id") %>% 
  ggplot(data = .) +
  geom_boxplot(aes(x = rural_residence, y = measured_QOL, fill = rural_residence))

```

- Smoking may influence this association:  

```{r}

redcap_subjects %>%
  left_join(redcap_visits, by = "subject_id") %>% 
  ggplot(data = .) +
  geom_boxplot(aes(x = rural_residence, y = measured_QOL, fill = rural_residence)) +
  facet_wrap(facets = ~ smoker, labeller = label_both)

```



- We identified an association between visit frequency and quality of life: 

```{r}
redcap_subjects %>%
  full_join(redcap_visits, by = "subject_id") %>% 
  group_by(subject_id) %>%
  summarise(n_visits = n(),
            median_QOL = median(measured_QOL, na.rm = TRUE),
            rural_residence = unique(rural_residence),
            smoker = unique(smoker)) %>%
  ggplot(data = .) +
  geom_point(aes(x = median_QOL, y = n_visits, color = rural_residence)) +
  geom_smooth(method = "lm", aes(x = median_QOL, y = n_visits, color = rural_residence)) +
  facet_wrap(facets = ~ smoker, labeller = label_both)


```

